Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-20 paper/ms.tex
starting to include Mark's comments

The first observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA with  $77$\AA width,
corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
$h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a
total  $2161$  LAEs with an observed equivalent width larger than $190$\AA 
over a total survey area of $2.42$ deg$^{2}$ that includes 12 sub-fields, 
this corresponds to average surface number density of $0.20\pm 0.01$
arcmin$^{-2}$.

@@

@@

Next we construct mock surveys by making groups of $12$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping of the $11$
mock fields into a mock catalog is done in two different ways. The
first is called {\texttt match}, it follows the clustering of the
observational fields. From the $12$ mock fields, $7$ are constructed
from contiguous fields in the simulation to mimic the SSA22 region,
$3$ are also contiguous between them but not to the first $7$ fields
to mimic the SXDS fields and finally $2$ non-contiguous fields to
imitate the SDF and GOODS-North field.  The second way to group the
mock fields is called {\texttt   random}, whereby all the $11$ fields
are selected in such a way as to avoid that any two volumes are
contiguous. In this \documentname we only report the results obtained
by the {\texttt match} method and mention explicitly differences
observed with the {\texttt random} selection.

>>>>

The first observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA with  $77$\AA width,
corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
$h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a
total  $2161$  LAEs with an observed equivalent width, in the observer
frame, larger than $190$\AA 
over a total survey area of $2.42$ deg$^{2}$ that includes 12 sub-fields, 
this corresponds to average surface number density of $0.20\pm 0.01$
arcmin$^{-2}$.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{./plots/Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt match}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern in the
  {\texttt match} method.}
\end{center} 
\end{figure*}

@@

Next we construct mock surveys by making groups of $12$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping of the $12$
mock fields into a mock catalog is done in two different ways. The
first is called {\texttt match}, it follows the clustering of the
observational fields. From the $12$ mock fields, $7$ are constructed
from contiguous fields in the simulation to mimic the SSA22 region,
$3$ are also contiguous between them but not to the first $7$ fields
to mimic the SXDS fields and finally $2$ non-contiguous fields to
imitate the SDF and GOODS-North field.  The second way to group the
mock fields is called {\texttt   random}, whereby all the $12$ fields
are selected in such a way as to avoid that any two volumes are
contiguous. In this \documentname we only report the results obtained
by the {\texttt match} method and mention explicitly differences
observed with the {\texttt random} selection.

We note that we use $15\times 12=144$ mock fields out of the total of $210$
available sub-volumes. The reason is that the {\texttt match}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed, making unusuable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt random} method in order to allow a
fair comparison between the two methods.
